Predicting the conformational preferences of proteins using a physics-based free energy method

### 2013-05-12 Paper/supporting_information.tex

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{T0538.pdf}
\end{center}
\caption{The native and three model structures for an engineered protein (PDB ID: 2L09 and CASP
    code:T0538). Models 1,2 and 3 are from the group PconsR, Shell and FOLDIT respectively.}
\label{fig:T0538}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{T0538.pdf}
\end{center}
\caption{The free energy based ranking of the experimental and three predicted structures for an engineered protein (PDB ID: 2L09 and CASP
    code:T0538). Models 1,2 and 3 are from the group PconsR, Shell and FOLDIT respectively. In this case, one of the predicted structure 
    was found to be more stable than the experimental strucre.}
\label{fig:T0538}
\end{figure}
